---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SF6Dvalues

<!-- badges: start -->
<!-- badges: end -->

The goal of SF6Dvalues is to provide calculators and tools for SF-6D value sets.

## Installation

You can install the most recent version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("uo-cmor/SF6Dvalues")
```

## Example

### S3 vector classes

The `SF12` and `SF6D` classes provide S3 vectors to store SF-12 responses and SF-6D profiles, respectively.

`SF12` vectors are created with `SF12()`:

```{r SF12}
library(SF6Dvalues)
SF12(Q1 = 3:5, Q2 = 1:3, Q3 = 1:3, Q4 = 1:3, Q5 = 1:3, Q6 = 1:3,
     Q7 = 1:3, Q8 = 1:3, Q9 = 1:3, Q10 = 1:3, Q11 = 1:3, Q12 = 1:3)
```

SF-12 questions can be labelled either Q1, Q2, ..., Q12 as above, or Q1, Q2a, Q2b, ..., Q7:

```{r SF12-alt}
SF12(Q1 = 3:5, Q2a = 1:3, Q2b = 1:3, Q3a = 1:3, Q3b = 1:3, Q4a = 1:3,
     Q4b = 1:3, Q5 = 1:3, Q6a = 1:3, Q6b = 1:3, Q6c = 1:3, Q7 = 1:3)
```

`SF6D` vectors can be constructed from SF-6D dimension levels with `SF6D()`:

```{r SF6D}
SF6D(PF = 1:3, RL = 1:3, SF = 1:3, PAIN = 1:3, MH = 1:3, VIT = 1:3)
```

Or from an `SF12` vector with `as_SF6D()`:

```{r as_SF6D}
sf12 <- SF12(Q1 = 3:5, Q2 = 1:3, Q3 = 1:3, Q4 = 1:3, Q5 = 1:3, Q6 = 1:3,
             Q7 = 1:3, Q8 = 1:3, Q9 = 1:3, Q10 = 1:3, Q11 = 1:3, Q12 = 1:3)
as_SF6D(sf12)
```

Or directly from SF-12 responses with `sf6d_profile()`:

```{r sf6d_profile}
sf6d_profile(Q1 = 3:5, Q2 = 1:3, Q3 = 1:3, Q4 = 1:3, Q5 = 1:3, Q6 = 1:3,
             Q7 = 1:3, Q8 = 1:3, Q9 = 1:3, Q10 = 1:3, Q11 = 1:3, Q12 = 1:3)
```

### SF-6D utility values

Utility values can be calculated either from an `SF6D` vector or directly from SF-12 responses. At this stage, only the original Brazier & Roberts UK population value set is available.

```{r utility}
sf6d <- SF6D(PF = 1:3, RL = 1:3, SF = 1:3, PAIN = 1:3, MH = 1:3, VIT = 1:3)
utility(sf6d)
```

```{r sf6d_utility}
sf6d_utility(Q1 = 3:5, Q2 = 1:3, Q3 = 1:3, Q4 = 1:3, Q5 = 1:3, Q6 = 1:3,
             Q7 = 1:3, Q8 = 1:3, Q9 = 1:3, Q10 = 1:3, Q11 = 1:3, Q12 = 1:3)
```
